### 2012-09-11 inst/examples/figure3.Rmd
new method added

```{r deterministic}
pdfn <- function(P, s){
     dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

>>>>

```{r deterministic}
pdfn <- function(P, s){
     dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn, sigma_m=.5, sigma_i=.5)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````
